\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-01-27 papers/jss/article.Rnw
Add two words suggested by Phillip for clarity.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@864 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

After importing proto files, the corresponding message descriptors are
available from the \code{RProtoBuf:DescriptorPool} environment in 
the \proglang{R} search path.  This environment is implemented with the 
user-defined tables framework from the \pkg{RObjectTables} package
available from the OmegaHat project \citep{RObjectTables}.  Instead of
being associated with a static hash table, this environment
dynamically queries the in-memory database of loaded descriptors
during normal variable lookup.

>>>>

After importing proto files, the corresponding message descriptors are
available by name from the \code{RProtoBuf:DescriptorPool} environment in 
the \proglang{R} search path.  This environment is implemented with the 
user-defined tables framework from the \pkg{RObjectTables} package
available from the OmegaHat project \citep{RObjectTables}.  Instead of
being associated with a static hash table, this environment
dynamically queries the in-memory database of loaded descriptors
during normal variable lookup.
